Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-24 article.tex
discussion pre reference insertion and extrapolation

This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of BNs created with assistance from industry input. These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing. A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical nature as one of the most interconnected variables. The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil. This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate.

Of further significance was the management of pests and diseases, market pressures and climate. With these external influences being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use. In particular, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease TODO:. Of great concern to climate was how it influenced water availability, pest/disease pressures, and its overall contribution to vineyard health. Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change TODO:. In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield, erosion, and are further determinants of chosen grape varieties TODO:. The BN models capture the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.

The case study highlighted the direct influences on environmental sustainability, where environmental sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors. A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts. The model emphasised the need for balanced and regulated agrochemical practices; and especially for those to be followed appropriately. TODO: A literature review regarding this does here TODO:.

@@

The BN models provide structure to the broader way of how how the major factors within literature interact, offering a clearer understanding of their interdependencies and relative sensitivity with regard to environmental sustainability as an outcome. The existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study. The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered. A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships TODO:.

@@

Comparison with Previous Research:

    How do the results of this study compare with existing literature on sustainability in viticulture?
    What consistencies and discrepancies are observed between our findings and those reported in previous studies?
    What might explain any differences between our results and those of other studies?

Explanation of Unexpected Findings:

    Were there any unexpected or anomalous findings in the study?
    What potential explanations can be proposed for these unexpected results?
    How do these findings impact the overall conclusions of the study?

Implications of the Study:

    What are the broader implications of the study's findings for the field of viticulture and environmental sustainability?
    How might these results inform practical applications in vineyard management and policy-making?
    What theoretical contributions does this study make to the understanding of sustainability in agriculture?

Limitations:

    What are the main limitations of this study?
    How do these limitations affect the interpretation and generalizability of the results?
    What methodological or contextual factors should be considered when applying these findings to other regions or contexts?

Suggestions for Future Research:

    What gaps in the current knowledge were identified through this study?
    What specific areas or questions should future research focus on to build upon these findings?
    What methodological improvements or alternative approaches could enhance future studies on this topic?

Conclusions:

    What are the primary conclusions drawn from this study?
    How do these conclusions integrate with the broader body of knowledge on environmental sustainability in viticulture?
    What are the key takeaways for stakeholders in the viticulture industry and for future research directions?

>>>>

This investigation highlights the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of BNs created with assistance from industry input. These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing. A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical importance as one of the most interconnected variables. The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil. This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate TODO:.

Of further significance was the management of pests and diseases, market pressures and climate. With these external influences being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use. In particular, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease TODO:. Of great concern to climate was how it influenced water availability, pest/disease pressures, and its overall contribution to vineyard health. Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change TODO:. In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield, erosion, and are further determinants of chosen grape varieties TODO:. The BN models captured the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.

The case study highlighted the direct influences on environmental sustainability, where environmental sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors. A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts. The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices to be followed appropriately. TODO: A literature review regarding this does here TODO:.

@@

The BN models provide structure to the broader way of how the major factors within literature interact, offering a clearer understanding of their interdependencies and relative sensitivity with regard to environmental sustainability as an outcome. The existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study. The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered. A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships TODO:.

By linking fuel and electricity use with well-studied factors like water and climate, the BN model broadens the scope of sustainability research in viticulture, emphasising the interconnected nature of these challenges. Integrating elements which play critical roles in vineyard operational decisions such as tractor, fuel and electricity use, which were more peripheral within the bibliometric analysis, to central themes like water, pests/disease and climate offered a holistic view of sustainability in winegrowing. The model demonstrated how fuel, tractor, and electricity use are intertwined with factors such as water and climate through propagation. Even though environmental sustainability was not highly sensitive to such factors, they directly relate to operational decisions that can be influenced by growers over a season. For example, electricity and fuel use are crucial for irrigation systems, as well as fuel use and tractors required for operations linked to soil preparation, management, and pest/disease control actions. Notably these operational decisions can be preventative or reactionary within a season TODO:. With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (water, climate and disease TODO: check these connections) particularly all of which are affected by climate TODO:. Additionally, the need to adapt to changing climate conditions can drive increased use of fuel and electricity, potentially exacerbating greenhouse gas emissions. The findings align with TODO:, suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practices TODO:. This integrated perspective is crucial for developing effective strategies to enhance the sustainability of the winegrowing industry.

The integration of expert knowledge was an essential part of constructing these BNs, particularly in defining the structure of the network and the CPTs. However, even within this analysis, disagreements were present amongst the panel especially as the models became more granular. The model is limited by the knowledge of the expert panel and by its specificity to the Australian, and further the Coonawarra context. The model created is also limited, in that, it solely represents the outcomes of a single season in isolation. No further accounting for past or future factors that may affect vineyard outcomes or decisions were considered. A dynamic Bayesian network could potentially address this issue but would require further investigations regarding the temporal factors that occur between seasons. Although this is a limitting factor, the model created within this study could still operate as the central static consideration between these temporal factors if future research was conducted. Similarly, spatial influences are also difficult to generalise to. Factors influencing sustainability in one winegrowing region may differ significantly from those in another region due to variations in climate, soil types, management practices, and economic conditions. Therefore, the applicability of the BN developed for the Coonawarra region does not extend seamlessly to other wine regions. The more general model for Australia would also need to be altered to generalise to other countries due to the wide and varying circumstances that exist from country to country.

@@
